---
title: "Informe de estadistica descriptiva"
author: "Harbey Emir Cely"
date: "12/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Medidas de tendencia central y dispersión
### R Markdown

El presente informe evidencia las caracteristicas básicas de las series x, y ,z. Por ejemplo, para calcular un promedio usamos la fórmula $\bar{x}=\sum_{i=1}^n x_i/n$ 

$\star\dagger\star$ <http://rmarkdown.rstudio.com>.
<https://es.wikipedia.org/wiki/Ayuda:Uso_de_LaTeX>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:
```{r}
str(cars)
attach(cars)
names(cars)

# Coeficiente de asimetria
cv_speed = sd(cars$speed) / mean(cars$speed)
cv_distance = sd(cars$dist) / mean(cars$dist)  # varía mas la distancia, segun el CV
cars
```


```{r include=FALSE}
# No muestra el codigo
cv_distance
cv_speed
```
```{r echo=FALSE}
# Coeficiente de asimetria
cv_speed = sd(cars$speed) / mean(cars$speed)
cv_distance = sd(cars$dist) / mean(cars$dist)  # varia mas la distancia, segun el CV
```
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
hist(cars$dist, xlab = "Distancia", ylab = "frecuencia",
     main = "Histograma de Distancia", col = "gold")
hist(cars$speed, xlab = "Velocidad", ylab = "frecuencia",
     main = "Histograma de Velocidad", col = "cyan")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
